\chapter{Preliminary Work, Background and Motivation}

Here we need to talk about the original intent of the project.

\section{The Ti$\text{O}_\mathbf{2}$/Ti Interface System}

A description of the initial problem upon which the project was based.

\section{Initial Attempts to Model the Ti$\text{O}_\mathbf{2}$/Ti Interface System}
\subsection{The Difficulties of Nonequilibrium Statistical Mechanics}
\subsection{Dynamics of Ionic Crystals}
Maybe mention Ewald sums, and the other issues with computations about materials.
\subsection{Initial Work Done with MD}
I used some LAMMPS code to try to work with MD initially; melts and things.
\subsection{The Problems with MD}
Need to explain why issues with using MD, and why I eventually decided it was not a useful technique for this problem; in particular, why MD is fundamentally flawed as a concept.

\section{Simple Large-Scale Models of the Ti/O/Nb Interacting System}
I had a think about various methods I could use to tackle the system in question, and decided that the approach would would be most likely to bear fruit would be a continuum-modelled bulk PDE system with appropriate boundary conditions between
phases.
\subsection{Proposed Linear System}
Simplest possible model, and why it failed.
\subsection{Attempts to create a Suitable Nonlinear System}
Talk about why nonlinearity is necessary (as in, it just spits out the previous system again), and the difficulties of parametrising it.
\subsection{Parametrisation from a Microscopic Model}
Talk about the Dresden conference and what I learned from it.

\section{The Sticky Particle Model}
\subsection{Model Motivation}
As in, why this is a good start in 1d.
\subsection{Model Definition}
\subsection{Model Properties}
Including Detailed Balance, symmetry, ``locality''. Also mention that it is a Markov process.
\subsection{Relation to Existing Literature}
\subsection{Generalisation to Higher Dimensions}
Including a proof of detailed balance in arbitrary dimensions (on square lattice).

\section{Implications of Initial Work for the PhD Direction}
\subsection{Why the Change of Direction?}
Essentially, why trying to solve this particular problem is actually kind of silly, and why having a better theory of driven lattice flows would be more useful.
\subsection{Why Investigate Flow in the SPM?}
Talk about how boundary-condition-induced flow on systems that would otherwise obey detailed balance hasn't really been done before.
Bring it around to the question:
``Can we have interesting dynamics in a model which is symmetric and obeys detailed balance?''