Given that \texttt{KMCLib} has a Python frontend, a language with which I was not familiar, I took SUPA Python course this year. Other than that, I have attended no other courses, since, including that,
I believe I have already met all of my SUPA requirements.

As of yet, I have no publications. However, I would like to be ready to publish on the subject of the phenomenology of the one-dimensional lattice model described in~\ref{sec: modelChoice} by the end of the Summer.
In order to do this, I have the following short-term goals:
\begin{enumerate}
 \item Get the code working properly and stably. The input files have become a bit of a mess as I have experimented with them and need to be cleaned. Also the computations are currently memory-limited, which is not a great situation
 from a scaling-up perspective, so I need to develop cleverer ways of taking, storing and processing results.
 \item I need to work out how to port the code to some cluster in order to perform large-scale calculations; currently I am just running it on my laptop. I believe \texttt{Eddie3} would be a good choice of machine. In order to
 be able to run on such a system, I will need to tweak the code further.
 \item Once I have the capability to do lots of calculations fairly fast, I would like to firmly establish what the system does in equilibrium (as in, does it obey equation~\ref{eq: eqmBehaviour}?), and then move onto investigating dynamical
 behaviour in which Oxygen is driven through the system via concentration gradients. At that point we can compare to the mean-field long-wavelength PDE in equation~\ref{eq: longRangePDE}.
\end{enumerate}
Once I have done these things, I think that will be enough to publish in a paper.

I'm not entirely sure what to do after that; I will probably be in a better position to plan my next moves once this is done. Certainly I would like to extend the model to include alloying atoms such as Nickel, and it would also
be good to extend the model to three-dimensions, to make sure the behaviour isn't that different from that observed in one-dimension. I would like to have at least made the Nickel extension by the end of my PhD.